Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-07 paper-kelompok/main.tex
Add Hardware Assembly subsection

@@

>>>>

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.27]{dmf-hardware-scheme.png}}
    \caption{The main components of the proposed device.}
    \label{dmf-hardware-scheme}
    \end{figure}

@@

\subsection{Hardware Assembly}
Using Autodesk Fusion 360 software, the body and individual parts of the portable visible spectrophotometer were created and 3D printed.
The primary body, the optical light path, and the lamp holder were all 3D printed components.
Fig.~\ref{hardware} displays internal components of the device.
A polylactic acid (PLA) filament in black was used due to the need of low light reflectance.
Electronic parts like printed circuit boards (PCBs) and optical parts were placed inside the main body.

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{hardware-2.jpg}}
    \caption{Overview of the device's internal components.}
    \label{hardware}
    \end{figure}
